---
title: "Data Analysis and Storytelling Project"
author: "Your Name"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output: pdf_document
---

```{r Setup, include = FALSE}
knitr::opts_chunk$set(tidy.opts = (list(width.cutoff = 60,
                                        blank = TRUE)),
                      echo = TRUE,
                      error = TRUE)
```

[DELETE BEFORE SUBMITTING]

For Milestone 3:

- Replace all template prompts and instructions with your own work.
- Complete the Introduction, Dataset Description, Research Questions, Variables Used, and Planned Analysis sections.
- Leave the Code, Visualization, and Discussion sections empty.

Before submitting the final project:

- Remove all Planned Analysis sections.

# Introduction

**[DELETE THESE INSTRUCTIONS BEFORE SUBMITTING MILESTONE 3]**

Write one or two paragraphs introducing your project. Explain the purpose of the analysis and provide a brief overview of the dataset you selected.

# Dataset Description

**[DELETE THESE INSTRUCTIONS BEFORE SUBMITTING MILESTONE 3]**

Write one or two paragraphs describing your dataset and explaining why you selected it.

Include:

- Who or what the data was collected for
- The purpose of the data collection
- The unit of observation (what each row represents)
- The total number of observations in the dataset
- Any observations that have been removed (or will be removed) and why
- The key variables relevant to your analysis

## Variables Used

**[DELETE THESE INSTRUCTIONS BEFORE SUBMITTING MILESTONE 3]**

Replace the example table below with information about your dataset.

| Variable Name | Data Type | Description |
|---------------|-----------|-------------|
| example_var | Numeric | Example description |

# Research Question 1

## Question

**[DELETE THESE INSTRUCTIONS BEFORE SUBMITTING MILESTONE 3]**

Write a research question that investigates a relationship between two or more variables.

## Variables Used

**[DELETE THESE INSTRUCTIONS BEFORE SUBMITTING MILESTONE 3]**

List the variables that will be used to answer this research question and briefly describe their role in the analysis.

| Variable Name | Role in Analysis |
|---------------|------------------|
|               |                  |

## Planned Analysis (Milestone 3 Only — Remove Before Final Submission)

**[DELETE THESE INSTRUCTIONS BEFORE SUBMITTING MILESTONE 3]**

Describe how you plan to answer this question.

Include:

- The variables that will be used
- The relationships or comparisons you plan to investigate
- The visualizations you plan to create
- How the analysis will help answer the question

## Code

```{r}
```

## Visualization

```{r}
```

## Discussion

**[COMPLETE IN MILESTONE 4]**

# Conclusion

**[COMPLETE IN MILESTONE 4]**

**[DELETE THESE INSTRUCTIONS BEFORE SUBMITTING MILESTONE 3]**

Summarize the main findings from your analysis.

Consider:

- What patterns, trends, or relationships were observed?
- Which research questions were answered most clearly?
- What limitations should be considered when interpreting the results?
- What additional questions or analyses could be explored in the future?