---
title: Example Analysis Notebook Setup
editor: source
---

## Introduction

This project explores trends in restaurant menu items using nutritional information collected from several national restaurant chains. The goal of the analysis is to identify patterns in menu item calories and investigate how calorie counts vary across different restaurants and menu categories. Understanding these patterns may provide insight into differences in restaurant offerings and nutritional content.

## Dataset Description

This dataset contains nutritional information for menu items offered by several restaurant chains. The data was collected to provide consumers with information about the nutritional content of restaurant meals.

Each row in the dataset represents a single menu item. The dataset contains 9,569 observations. No observations have been removed at this stage of the analysis.

The variables most relevant to this project include the restaurant name, menu category, and calorie count. These variables will be used to investigate differences in nutritional content across restaurants and menu item types.

### Variable Documentation

| Variable Name | Data Type | Description                         |
| ------------- | --------- | ----------------------------------- |
| restaurant    | Character | Name of the restaurant chain        |
| item_name     | Character | Name of the menu item               |
| category      | Character | Menu category for the item          |
| calories      | Numeric   | Number of calories in the menu item |

## Research Question 1

### Question

How does the average calorie content of menu items vary across restaurants?

### Variables Used

List the variables that will be used to answer this research question and briefly describe their role in the analysis.

| Variable Name | Role in Analysis                                   |
| ------------- | -------------------------------------------------- |
| restaurant    | Grouping variable used to compare restaurants      |
| calories      | Numerical variable used to measure calorie content |

### Planned Analysis

To answer this question, I will compare the average calorie content of menu items across restaurants. I will calculate summary statistics, including the mean and median calorie counts for each restaurant. I will also create a visualization that compares calorie distributions across restaurants. This analysis will help identify whether some restaurants tend to offer higher-calorie menu items than others.

### Code

```{r}
```

### Visualization

```{r}
```

## Conclusions

## Course Reflection
